FraCaS: 80 percent complete

### 2019-01-21 paper2018/paper.tex
oops, compilation
typography
more typography

\paragraph{anaphora} Thanks to the above system, we can handle many
anaphoric cases, including E-Type and Donkey pronouns. Indeed, even
objects which have no syntactic representation can be added to the
environment. We follow here the general pattern outlined by
\citet{unger:2011}. However, we use a more general scope-extension
mechanism, which allows us to support examples such as the following:
\item[FraCaS 122]
P1	Every committee has a chairman.\\
P2	He is appointed its members.\\
H 	Every committee has a chairman appointed by members of the committee. 
\end{lingex}
In the above example, the pronoun ``he'' is allowed to refer to the
object quantified over by ``every'', whose scope is extended
accordingly.

@@

We evaluated FraCoq against 8 sections of the FraCaS test suite, for a
total of 259 examples. We excluded only section 7, ``temporal reference''. The reason for
doing so is that, in our view, it contains too many examples which
require \textit{ad-hoc} treatment, and thus makes little sense to
include without complementing it with a more thorough suite which
captures a more complete landscape of the phenomena that section 7
touches.

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & \# examples & Ours     & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74) & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82      & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20) & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87      & .56    & .48  & .45  &  -       \\
7 & Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
8 & Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92      & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
  &              &             & (259)    & (174)  & (174)& (174)& (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of examples shown in the
    third column, the actual number of examples attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}. A dash indicates that no attempt was made
    for a given section. }
  \label{tbl:results}
\end{table}

@@

\paragraph{error analysis}
Our system fails to classify correctly 28 cases out of 259.  We give
here a summary of the missing features which are responsible for the
biggest number of failures. The one biggest source of error is an
incomplete handling of group readings. (FraCaS
013,014,046,084,111,124,126,127,137,171,172,191,193,195,243,250,333,346). These
are cases where a syntactic conjunction of individuals is treated as a
semantic group, or where precise counting of the members of a group is
necessary.  Other problematic cases are where a definite plural does
not have a universal reading (091,094,095) --- these require an
analysis at the pragmatic level, which our system lacks. Additionally,
neither measure phrases (242) nor attributive comparatives (244,245)
are handled.

>>>>

\paragraph{anaphora} Thanks to the above system, we can handle many
anaphoric cases, including E-Type and Donkey pronouns. Indeed, even
objects which have no syntactic representation can be added to the
environment. We follow here the general pattern outlined by
\citet{unger:2011}. However, we use a more general scope-extension
mechanism, which allows us to support examples such as the following:
\begin{lingex}
\item[FraCaS 122]
P1	Every committee has a chairman.\\
P2	He is appointed its members.\\
H 	Every committee has a chairman appointed by members of the committee. 
\end{lingex}
In the above example, the pronoun ``he'' is allowed to refer to the
object quantified over by ``every'', whose scope is extended
accordingly.

@@

We evaluated FraCoq against 8 sections of the FraCaS test suite, for a
total of 259 cases. We excluded only section 7, ``temporal reference''. The reason for
doing so is that, in our view, it contains too many examples which
require \textit{ad-hoc} treatment, and thus makes little sense to
include without complementing it with a more thorough suite which
captures a more complete landscape of the phenomena that section 7
touches.

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & {\kern -1em} \# cases & Ours     & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74) & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82      & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20) & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87      & .56    & .48  & .45  &  -       \\
7 & Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
8 & Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92      & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
  &              &             & (259)    & (174)  & (174)& (174)& (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases shown in the
    third column, the actual number of test cases attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}. A dash indicates that no attempt was made
    for a given section. }
  \label{tbl:results}
\end{table}

@@

\paragraph{error analysis}
Our system fails to classify correctly 28 cases out of 259.  We give
here a summary of the missing features which are responsible for the
biggest number of failures. The one biggest source of error is an
incomplete handling of group readings. (FraCaS
013, 014, 046, 084, 111, 124, 126, 127, 137, 171, 172, 191, 193, 195, 243, 250, 333, 346). These
are cases where a syntactic conjunction of individuals is treated as a
semantic group, or where precise counting of the members of a group is
necessary.  Other problematic cases are where a definite plural does
not have a universal reading (091,094,095) --- these require an
analysis at the pragmatic level, which our system lacks. Additionally,
neither measure phrases (242) nor attributive comparatives (244,245)
are handled.
